Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model

### 2012-02-05 Multiresolution_framework/ltx/manuscript.tex
minor edits

 where $\left[\Gamma(r')\right]_{:i}$ denotes the $i$th column of  $\left[\Gamma(r')\right]$ giving

@@

The multi-resolution approximation using B-spline functions is completed by defining a two-scale relation pair, which relates the scaling functions and the wavelets at a given scale with the scaling function at the next higher scale. This is important for constructing the wavelets. For cardinal B-spline scaling and wavelet functions of order $m$ the two-scale relation pair takes the form of
\begin{align}
 N_{m}\left(r\right)&=\sum_{n=0}^{m} \left[\mathbf p\right]_n N_{m}\left(2r-n\right) \label{eq:MRA-TwoScalepair1} \\
  \varphi_{m}\left(r\right) &= \sum_{n=0}^{3m-2} \frac{\left(-1\right)^n}{2^{m-1}} \left[\mathbf q\right]_n N_{m}\left(2r-n\right)\label{eq:MRA-TwoScalepair2},
 \end{align}
where 
 \begin{align}
\left[\mathbf p\right]_n&=2^{-m+1} \binom{m}{n} \quad \text{ $0\le n\le m$} \label{eq:MRA-TwoScalepair1coefs}\\
\left[\mathbf q\right]_n&= \sum_{l=0}^{m} \binom{m}{l} N_{2m}\left(n-l+1\right), \,  \text{ $0\le n\le 3m-2$}\label{eq:MRA-TwoScalepair2coefs}
 \end{align}
and $\left[\cdot\right]_n$ denotes the $n$-th element of the vector coefficients \citep{Chui1992}. \dean{Need to explicitly say why this is important and what this gives us here.}

Fig.~\ref{fig:MRA-Figure1} shows the cubic B-spline scaling function and its associated wavelet function with dilation and translation parameters set to zero. Note in general the supports of B-spline scaling and wavelet functions are given by 
\begin{align}
	\mathrm{supp}(N_{m;j,l})&=\left[\frac{l}{2^j},\frac{m+l}{2^j}\right] \label{eq:ScalingSupport}\\  
  \mathrm{supp}(\varphi_{m;j,l})&=\left[\frac{l}{2^j},\frac{2m-1+l}{2^j}\right],\label{eq:WaveletSupport}
	\end{align}    
where subscripts $j$ and $l$ in Eqs.~\eqref{eq:ScalingSupport} and \eqref{eq:WaveletSupport} are introduced to $N_{m}(r)$ and $\varphi_{m}(r)$ to indicate the scale and translation parameters as defined in Eqs~\eqref{eq:generalscalingfinction} and \eqref{eq:generalwaveletfinction}. 
\begin{figure}[!t]
\centering
\includegraphics{./Graph/fig4.pdf}
% \includegraphics{./Graph/Figure1b.pdf}
\caption{{\bf Examples of B-spline scaling and wavelet functions}. (\textbf{A}) The cubic B-spline scaling function. (\textbf{B}) The corresponding wavelet function.}
\label{fig:MRA-Figure1}
\end{figure}

@@

	  \mathcal{F}(\varphi_{m}\left(r\right)) &= \sum_{n=0}^{3m-2} \frac{\left(-1\right)^n}{2^{m-1}} \left[\mathbf q\right]_n \mathcal{F}\left(N_{m}\left(2r-n\right)\right) \nonumber\\
	&=\sum_{n=0}^{3m-2} \frac{\left(-1\right)^n}{2^{m}} \left[\mathbf q\right]_n \mathrm{exp}(-2\pi in\nu)\left(\frac{1-\mathrm{exp}(-\pi i \nu)}{\pi i\nu}\right)^m.\label{eq:MRA-Wavelettransform}

>>>>

 where $\left[\Gamma(r')\right]_{:i}$ denotes the $i$-th column of  $\left[\Gamma(r')\right]$ giving

@@

The multi-resolution approximation using B-spline functions is completed by defining a two-scale relation pair, which relates the scaling functions and the wavelets at a given scale with the scaling function at the next higher scale. This is important for constructing the wavelets. For cardinal B-spline scaling and wavelet functions of order $m$ the two-scale relation pair takes the form of
\begin{align}
 N_{m}\left(r\right)&=\sum_{n=0}^{m} \left[\mathbf p\right]_n N_{m}\left(2r-n\right) \label{eq:MRA-TwoScalepair1} \\
  \varphi_{m}\left(r\right) &= \sum_{n=0}^{3m-2}  \left[\mathbf q\right]_n N_{m}\left(2r-n\right)\label{eq:MRA-TwoScalepair2},
 \end{align}
where 
 \begin{align}
\left[\mathbf p\right]_n&=2^{-m+1} \binom{m}{n} \quad \text{ $0\le n\le m$} \label{eq:MRA-TwoScalepair1coefs}\\
\left[\mathbf q\right]_n&= \left(-1\right)^n{2^{-m+1}}\sum_{l=0}^{m} \binom{m}{l} N_{2m}\left(n-l+1\right), \,  \text{ $0\le n\le 3m-2$}\label{eq:MRA-TwoScalepair2coefs}
 \end{align}
and $\left[\cdot\right]_n$ denotes the $n$-th element of the vector coefficients \citep{Chui1992}. \dean{Need to explicitly say why this is important and what this gives us here.}

Fig.~\ref{fig:MRA-Figure1} shows the cubic B-spline scaling function and its associated wavelet function with dilation and translation parameters set to zero. Note in general the supports of B-spline scaling and wavelet functions are given by 
\begin{align}
	\mathrm{supp}(N_{m;j,l})&=\left[\frac{l}{2^j},\frac{m+l}{2^j}\right] \label{eq:ScalingSupport}\\  
  \mathrm{supp}(\varphi_{m;j,l})&=\left[\frac{l}{2^j},\frac{2m-1+l}{2^j}\right],\label{eq:WaveletSupport}
	\end{align}    
\parham{where subscripts $j$ and $l$ in Eqs.~\eqref{eq:ScalingSupport} and \eqref{eq:WaveletSupport} are introduced to $N_{m}(r)$ and $\varphi_{m}(r)$ to indicate the scale and translation parameters as defined in Eqs~\eqref{eq:generalscalingfinction} and \eqref{eq:generalwaveletfinction}.}
\begin{figure}[!t]
\centering
\includegraphics{./Graph/fig4.pdf}
% \includegraphics{./Graph/Figure1b.pdf}
\caption{{\bf Examples of B-spline scaling and wavelet functions}. (\textbf{A}) The cubic B-spline scaling function. (\textbf{B}) The corresponding wavelet function.}
\label{fig:MRA-Figure1}
\end{figure}

@@

	  \mathcal{F}(\varphi_{m}\left(r\right)) &= \sum_{n=0}^{3m-2} \left[\mathbf q\right]_n \mathcal{F}\left(N_{m}\left(2r-n\right)\right) \nonumber\\
	&=\sum_{n=0}^{3m-2} \left[\mathbf q\right]_n \mathrm{exp}(-2\pi in\nu)\left(\frac{1-\mathrm{exp}(-\pi i \nu)}{\pi i\nu}\right)^m.\label{eq:MRA-Wavelettransform}
